Nail: A practical interface generator for data formats

### 2014-05-01 paper/osdi14/eval.tex
Eval-security

XXX refer back to \S\ref{s:motivation}.

Nail parsers are immune by design to vulnerabilities like these 14.
Because Nail's generated code checks offsets before reading and does not
expose any untrusted pointers to the application, it protects against
memory corruption attacks by design.

Nail also protects against parser ambiguity vulnerabilities.

Instead of both components containing
an ad-hoc archive implementation, a single Nail grammar would be reusable
across both implementations.

>>>>

In \S\ref{s:motivation}, we found 14 input handling vulnerabilities related to ZIP files.

Ten of these vulnerabilities involved memory corruption during input handling.
Because Nail's generated code checks offsets before reading and does not
expose any untrusted pointers to the application, it is immune against
memory corruption attacks by design.

Nail also protects against parsing ambiguity vulnerabilities like the four others we studied. First,
Nail grammars explicitly encode duplicated information such as the redundant length fields in ZIP
that caused a vulnerability in the Python ZIP library. Second, the other three vulnerabilities exist
because multiple implementations of the same protocol disagree on some inputs. Hand-written protocol
parsers are not very reuseable, as they build application specific data structures and are tightly
coupled to the rest of the code. Nail grammars, however, can be re-used between applications,
avoiding protocol misunderstandings.

### 2014-05-01 paper/osdi14/motivation.tex
Eval-security

The ZIP format has been associated with many vulnerabilities, and the
PROTOS Genome project found numerous security vulnerabilities in most
implementations of ZIP and other archive formats that are directly
related to input handling.
\XXX[what is the PROTOS Genome project?]

@@

\paragraph{Vulnerability mitigation.}

>>>>

The ZIP format has been associated with many vulnerabilities, and the
PROTOS Genome project~\cite{protoc-c10-archive} found numerous security vulnerabilities in most
implementations of ZIP and other archive formats that are directly
related to input handling.

@@

\paragraph{Vulnerability classes.}
